%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Intern, Big Data Experience Lab} % Job title
    {Adobe} % Organization
    {Bangalore, India} % Location
    {May - July 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Geo-fence is a virtual parameter that triggers notifications depending on entry, exit or dwell time of user. The project focused on analyzing customer’s historical app usage behavior to automatically learn geo-fences for selective geo-targeting.}
        \item {Geo-fences are created by identifying areas with high values of user interest. To unsheathe interest from sparse location tagged browsing data, algorithm captures intrinsic interest of user, trends at semantically similar locations and similarity between products and users.}
        \item {Achieved precision was 5 times higher than existing geo-fence. Created user-friendly marketer’s dashboard where marketer can manage geo-fence and get useful inferences about product sale. \underline{Patent is internally accepted by Adobe} and writing research paper is in process.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research and Developement Intern} % Job title
    {Pariksha.co} % Organization
    {Pune, India} % Location
    {May - July 2015} % Date(s)
    {
      \begin{cvitems} 
      	\item {Engineered an algorithm that adaptively recommend questions depending upon student’s performance and question ratings.}
      	\item {Modeled and programmed scalable adaptive question recommender system using GO language and MongoDB database as a micro service.}
      	\item {Implemented Pariksha Practice Section for adaptive content and a Gamification engine with impact on 20K students.}
      \end{cvitems}
    }
\end{cventries}
