%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
   {Member of Technical Staff} % Job title
   {Adobe Systems India Pvt. Ltd.} % Organization
   {July 2017 - ongoing} % Location
   {} % Date(s)
   {
   	\begin{cvitems}
   		\item {Developed POC of a unified \textbf{smart tool} for all annotation types (highlight, underline, strikethrough, polygons, and free pen). Trained a CNN for detecting type of tool given images of user drawings. Idea got selected for shipping with the March Release of Adobe Acrobat} %(\emph{video \ExternalLink})
   		\item {Developed an efficient algorithm for the synchronization of sticky comments between PDFNext(HTML based PDF format) and Classic PDF inside Adobe Acrobat. The challenge was to associate user click on HTML document to the most relevant textual/graphical content.}
   		\item {Fixed more than ten critical security vulnerabilites (buffer overflow vulnerabilities, javascript parameter tempering). Severity ranged from crash of the application on launching malicious pdfs to giving full read/write permissions of user to the attacker.}
   	\end{cvitems}
   }
   
  \cventry
    {Research Intern} % Job title
    {Adobe Systems India Pvt. Ltd.} % Organization
    {May - July 2016} % Location
    {
    	(
	    	\textbf{\href{https://research.adobe.com/project/smart-geo-fencing/}{project page} \ExternalLink},
	    	% \href{https://drive.google.com/file/d/1uoMtvSSBmur6VNDnTeImWG9TrFckfpQF/view?usp=sharing}{\textbf{paper \ExternalLink}}, 
	    	\href{https://drive.google.com/file/d/1nfCv13-7V3BElFPLBfFI\_LF0RRcsdNvy/view?usp=sharing}{\textbf{pres \ExternalLink}}
	    )
    }  % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {
%        	The project focused on analyzing customer’s historical app usage behavior to automatically learn geo-fences for selective geo-targeting
%        }
        \item {
			The aim was to assist marketers in creating \textbf{smarter geo-fences}. The project was focused on segmenting users based on their geo-distributions of mobile app activity, identifying points-of-interest and then suggesting geo-fences customized to each user segment.
        }
        \item { 
        	To unsheathe interest from sparse location tagged browsing data, algorithm captures intrinsic interest of user, trends at semantically similar locations and similarity between products and users
        }
        \item {
        	Achieved f1 score (24.89\%) was significantly higher than geofence designed using Matrix Factorization (18.16\%). 
        }
        \item {
        	 Project was showcased in \textbf{Adobe Tech Summit, 2017} ( \href{https://www.youtube.com/watch?v=PS0imh951ZE}{talk video \ExternalLink}) 
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research and Developement Intern} % Job title
    {Pariksha.co} % Organization
    {May - July 2015} % Location
    {} % Date(s)
    {
      \begin{cvitems} 
      	\item {Engineered an algorithm that adaptively recommend questions depending upon student’s performance and question ratings}
      	\item {Modeled and programmed scalable adaptive question recommender system using the GO language and MongoDB database as a micro service}
      	\item {Implemented Pariksha Practice Section for adaptive content and a Gamification engine with impact on more than 50K students}
      \end{cvitems}
    }
\end{cventries}



