I, Shubham Agrawal, am a 4th year undergraduate student pursuing a B.Tech in Computer Science with a
keen interest in the field of Machine Learning. Highly qualified and dedicated professors, coursework and
competitive environment of I.I.T. Kanpur has driven me to explore various areas in computer science including machine
learning. Problem-solving sessions, seminars, research days, workshops and guest lectures
organized by the SIGML - Special Interest Group in Machine Learning, always left me mesmerized by its
wide applicability.
\\
My interest in machine learning kindled during my 2nd year internship where I was given a task to model
an adaptive question recommender system that adaptively recognizes student’s capability and recommend
questions. Then on, I started exploring. I have done online introductory course on machine learning by
Andrew Ng. I have also done courses like Machine Learning Tools, Natural Language and Processing and
Recent Advances in Computer Vision. Course projects allowed me to implement and explore various machine
learning areas such as object detection and classification in images and videos, text summarization for large
documents.
\\
I have worked with Prof. Harish Karnick, Computer Science Department, I.I.T. Kanpur for three months
on Multiple Kernel Learning Algorithm. I learned about relative kernel hilbert spaces, hierarchical kernel
learning, kernel learning framework for multiple tasks [1]. I analyzed the effects of linear combinations of
sigmoid, rbf and polynomial kernels on SVM classifier. During my summer internship at Big Data Experience Lab, Adobe, I worked on creating data drive dynamic geo-fences for selective targeting. The Projectinvolves extracting user’s interest towards given product and location from sparse location tagged browsing
history. Then, geo-fences are generated that adapt with the changing interest of people. The project also
involved modeling interest of people based on trends at location and behavior of similar users.
\\
Currently, I am working under Prof. Purushottam Kar, Computer Science Department, I.I.T. Kanpur
where I am trying to find a low-rank model for fully connected layers in neural networks. I am primarily motivated by Robust PCA problem via outlier pursuit [3] which seeks to find the best (in the least-square-error
sense) low-dimensional subspace approximation to high-dimensional points after eliminating corruptions. I
think that a similar approach can be used to find low-rank weight matrix along with corruptions for reducing
memory and run-time of deep neural networks. I also find the work of Netrapalli et. al. [2] relevant where
they perform the same task in nonconvex optimization setting.
\\
I bring along a strong grasp of fundamentals in Computer Science and Mathematics, an aptitude for research and teamwork, a zest for challenges and an enthusiastic desire to learn all I can. I would like to take
with me, in addition to knowledge of machine learning, a network of strong and lasting relationships with my
mentors and colleagues. Research Fellows Program at Microsoft will help me interact with best researchers
across the globe and gain extensive research experience. As a highly motivated student to pursue research
in machine learning, I assure my full sincerity and hard work if given this wonderful opportunity.