I am graduating in July 2017 from IIT Kanpur with a B.Tech degree in Computer Science. I found about this job at your company website while searching for the full-time job opportunities. 
\\
\\
I've previously worked on e-commerce website data during the research internship at Adobe. We worked on creating smart geofences which can automatically segment users according to their purchase interest and identify appropriate time and location for targeting. All rules are algorithmically driven by data collected through an e-commerce retailer’s mobile application. Our prototype ``Data-driven dynamic geofences for selective targeting'' is patented internally at Adobe. 
At Pariksha.co - an E-learning startup, I designed Adaptive question recommendation service-REST API with its own token based authentication system using GO language and MongoDB database. I designed the backend of Practise Section and a Gamification engine to support the Practise Section with Global student rating system, User leaderboard on Redis server, badges and session wise achievement summaries. Pariksha's Practise Section is currently being used by over 20K students. Apart from these, learning environment at IIT Kanpur strengthened my computer science fundamentals. I scored an A grade in Algorithms and Advanced Algorithms course. I've also been awarded an A* grade for exception performance in Operating System course. 
\\
\\
I bring along a strong grasp of fundamentals in Computer Science, an aptitude for research and teamwork, a zest for challenges and an enthusiastic desire to learn all I can. I would like to gain, in addition to knowledge of developing complex software, a network of strong and lasting relationships with my mentors and colleagues. As a highly motivated engineer to pursue development career, I assure my full sincerity and hard work if given this wonderful opportunity. 