%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
   {Member of Technical Staff (Software Engineer)} % Job title
   {Adobe Systems India Pvt. Ltd.} % Organization
   {July 2017 - ongoing} % Location
   {} % Date(s)
   {
   	\begin{cvitems}
   		\item {
	   		Developed POC of a \textbf{unified annotation tool} which automatically detects the annotation user is trying to make. Trained CNN for detecting tool (highlight/underline/strikethrough/polygons) given user drawings and pdf context. Idea got selected for the March Release
   		}
   		\item {Engineered an efficient algorithm for the synchronization of sticky comments between PDFNext (HTML based PDF format) and Classic PDF inside Adobe Acrobat. The challenge was to associate user click on HTML document to the most relevant textual/graphical content.}
   		\item {Fixed more than ten critical security vulnerabilities (including buffer overflow vulnerabilities and javascript parameter tempering). Severity ranged from the crash of the application on launching malicious pdf to granting full read/write permissions of the user to the attacker.}
   	\end{cvitems}
   }
   
  \cventry
    {Research Intern} % Job title
    {Adobe Systems India Pvt. Ltd.} % Organization
    {May - July 2016} % Location
    {
    	(
	    	\textbf{\href{https://research.adobe.com/project/smart-geo-fencing/}{project page} \ExternalLink},
	    	% \href{https://drive.google.com/file/d/1uoMtvSSBmur6VNDnTeImWG9TrFckfpQF/view?usp=sharing}{\textbf{paper \ExternalLink}}, 
	    	\href{https://drive.google.com/file/d/1nfCv13-7V3BElFPLBfFI\_LF0RRcsdNvy/view?usp=sharing}{\textbf{pres \ExternalLink}}
	    )
    }  % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {
%        	The project focused on analyzing customer’s historical app usage behavior to automatically learn geo-fences for selective geo-targeting
%        }
        \item {
			The aim was to assist marketers in creating \textbf{smart geo-fences}. The project was focused on segmenting users based on their geo-distributions of mobile app activity, identifying points-of-interest and then suggesting geo-fences customized to each user segment.
        }
        \item { 
        	To unsheathe interest from sparse location tagged browsing data, algorithm captures intrinsic interest of user, trends at semantically similar locations and similarity between products and users
        }
        \item {
        	Achieved f1 score (24.89\%) was significantly higher than geofence designed using Matrix Factorization (18.16\%). 
        }
        \item {
        	 Project was showcased in Adobe Tech Summit, 2017 (an annual internal research and engineering conference) ( \href{https://www.youtube.com/watch?v=PS0imh951ZE}{talk video \ExternalLink}) 
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research and Development Intern} % Job title
    {Pariksha.co} % Organization
    {May - July 2015} % Location
    {} % Date(s)
    {
      \begin{cvitems} 
      	\item {Engineered an algorithm that adaptively recommends questions depending upon student’s performance and question ratings}
      	\item {Modeled and programmed scalable \textbf{adaptive recommender system} using the GO language and MongoDB database as a microservice}
      	\item {Implemented Pariksha Practice Section for adaptive content and a Gamification engine with impact on more than 50K students}
      \end{cvitems}
    }
\end{cventries}



