\cvsection{Projects}
\begin{cventries}
	%---------------------------------------------------------
	\cventry
	{Course Project under Dr. Gaurav Sharma} % Job title
	{Densecap with NMS Convenet} % Organization
	{Aug. - Nov. 2016} % Location
	{
		\textbf{\href{https://www.dropbox.com/s/5jidhqmthy9ks06/cs698-final-report-extended.pdf?dl=0}{report \ExternalLink}},
		\textbf{\href{https://www.dropbox.com/s/byn2z4o4yiwf00b/CS698\%20Final\%20PPT.pdf?dl=0}{pres \ExternalLink}}
	} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			%\item {Aim was to choose an SOA paper, implement/reproduce approximate results and finally go beyond that work.} 
			\item {Analyzed and extended the work ``DenseCap: Fully Convolutional Localization Networks for Dense Captioning". Reproduced the results on smaller 2 GB GPU which required a lot of optimizations (Originally, 12 GB Titan X GPU was used)}
			\item To discard test-time NMS in favor of a trainable spatial suppression layer, we used the ``Tyrolean network - A convolutional network for NMS"
			\item {Enhanced the \textbf{mAP} of densecap from \textbf{5.698 to 5.76}.}
		\end{cvitems}
	}
	
	%---------------------------------------------------------
	\cventry
	{Undergraduate project under Dr. Harish Karnick} % Job title
	{Multiple Kernel Learning} % Organization
	{Jan. - Apr. 2015} % Location
	{\href{https://www.dropbox.com/s/dg987vl0zdfh6kj/cs396-graduate-project.pdf?dl=0}{\textbf{report \ExternalLink}}} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			 \item {Explored relative reproducing kernel Hilbert space, multiple kernel learning algorithm, and hierarchical kernel learning.}
			 \item {Extracted surf and convolutional deep-net (pre-trained BVLC GoogleNet model) features for Caltech multiclass object classification dataset}
			 \item {Implemented \textbf{Simple MKL} algorithm and studied effects of linear combination of distinct kernels on SVM classifier}
%			 \item {
%			 	\href{https://www.dropbox.com/s/dg987vl0zdfh6kj/cs396-graduate-project.pdf?dl=0}{report \ExternalLink}
%			 }
		\end{cvitems}
	}
	
	\cventry
	{
		Course Project under Dr. Piyush Rai
	} % Job title
	{Poisson Matrix Factorization} % Organization
	{Jan. - May 2017} % Location
	{\textbf{\href{https://www.dropbox.com/s/a5gn52k0ggf8m5w/poisson-matrix-factorization.pdf?dl=0}{report \ExternalLink}}} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Studied various models for Bayesian recommender systems including poisson matrix factorization, hierarchical poisson matrix factorization, bayesian non-parametric poissonmatrix factorization}
			\item {Implemented and compared the performance of the three models on MovieLens 1M dataset. Also analyzed the effect of latent dimension on the models}
			\item {Learnt the use of auxilliary variables in variational inference to make the models locally conjugate and facilitate inference}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Course Project under Dr. Harish Karnick} % Job title
	{Automatic Abstract Generation for Research Papers} % Organization
	{Aug. - Nov. 2016} % Location
	{\textbf{\href{https://www.dropbox.com/s/h5jqpm20l8bhan6/G4-FinalReport.pdf?dl=0}{report \ExternalLink}}} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {
				The important sentences are extracted from the paper and fed to an abstractive model which outputs the final summary of the paper
			}
			\item {
				Word frequency based scores, text rank, and latent semantic analysis experimented for extraction. 
			}
			\item {
				Implemented RNN encoder-decoder network to generate the final abstract. The model was evaluated using ROGUE metric.
			}
		\end{cvitems}
	}	
	%---------------------------------------------------------
	\cventry
	{Course Project under Dr. Purushottam Kar} % Job title
	{Low-rank model for neural networks} % Organization
	{Aug. - Nov. 2016} % Location
	{
		\textbf{\href{https://www.dropbox.com/s/wb51nni96m6s1nr/Final\%20Project\%20Report.pdf?dl=0}{report \ExternalLink}}	
	} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item { 
				Implemented a module for decomposing the input weight matrix into a low rank and a sparse matrix.
			}
			\item { 
				Based on the paper - \textit{``Robust PCA problem via outlier pursuit"} which finds the low-dimensional subspace approximation to high dimensional points after eliminating corruptions.
			}
		\end{cvitems}
	}


	%---------------------------------------------------------
	
	\cventry
	{Course Project under Dr. Harish Karnick} % Job title
	{Object(Pedestrian/Two-Wheeler/Three-Wheeler) Detection in Surveillance Videos} % Organization
	{Jan. - Aug. 2016} % Location
	{
		\textbf{\href{https://github.com/submagr/MLT-Classifier}{code \ExternalLink}}, 
		\textbf{\href{https://www.dropbox.com/s/sh69si90hl7mtxr/MLTProjectReport.pdf?dl=0}{report \ExternalLink}}	
	} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Identified and classified objects into pedestrians, two-wheelers, three-wheelers and four-wheeler in surveillance video}
			\item {Performed background-foreground separation to identify moving objects. Used SURF and convolutional deep-net features (BVLC GoogleNet)}
			\item {Used decision tree, random forest and SVM (OVR and OVO) classifiers to predict labels}
		\end{cvitems}
	}
%	%---------------------------------------------------------
%	
%	
%	\cventry
%	{Course Project under Dr. Subhajit Roy} % Job title
%	{Go-Python-x86 Compiler Design} % Organization
%	{IIT Kanpur, India} % Location
%	{Jan. - Apr. 2016} % Date(s)
%	{
%		\begin{cvitems} % Description(s) of tasks/responsibilities
%			\item Implemented an end-to-end compiler for a subset of Go language and x86 architecture in python using PLY (python Lex-Yacc)
%			\item Provided support for multi-dimensional arrays, nested and recursive procedures etc. Used back tracking algorithm and done short circuiting
%		\end{cvitems}
%	}
%	
%	%---------------------------------------------------------
%	\cventry
%	{Course Project under Dr. Mainak Choudhari} % Job title
%	{NachOS} % Organization
%	{IIT Kanpur, India} % Location
%	{Jan. - Apr. 2016} % Date(s)
%	{
%		\begin{cvitems} % Description(s) of tasks/responsibilities
%			\item Extended the standard system call library of NachOS and implemented system calls pertaining to Fork, Exec, Join, Yield, Sleep and Exit
%			\item Implemented process scheduling algorithms: UNIX Scheduling, FIFO, Round Robin, Shortest Job First and Non-pre-emptive job scheduling
%			\item Programmed page replacement algorithms: Random Page Allocation, FIFO, LRU and LRU Clock to evaluate relative performances
%		\end{cvitems}
%	}
%	%---------------------------------------------------------
%	\cventry
%	{Course Project under Dr. Sandeep Shukla} % Job title
%	{Zoobar Secure} % Organization
%	{IIT Kanpur, India} % Location
%	{Jan. - Apr. 2016} % Date(s)
%	{
%		\begin{cvitems} % Description(s) of tasks/responsibilities
%			\item Extended zoobar web application to learn about various security concepts including buffer overrun attacks, xss, csrf and sql injection
%			\item Done privilege separation and server side sandboxing on OKWS web server. Created program analysis tools based on symbolic execution
%		\end{cvitems}
%	}
	
	%---------------------------------------------------------
	\iffalse
	\cventry
	{Subtitle Downloader} % Job title
	{Open Source Projects} % Organization
	{IIT Kanpur, India} % Location
	{Dec. 2013} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item Wrote a python script that scrapes and extract the subtitle from subscene.com.
		\end{cvitems}
	}
	
	\cventry
	{IITK FB Forum App} % Job title
	{} % Organization
	{} % Location
	{May 2014} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item Created an online discussion website for students and connected it with Facebook to make it more user friendly
			\item Used PHP and PostgreSQL for back-end and hosted application on Heroku. Used Facebook SDK for JavaScript for facebook login and Canvas frame for user interface
		\end{cvitems}
	}
	\fi
\end{cventries}