%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Shubham}{Agrawal}{ \urlstyle{same}\url{http://home.iitk.ac.in/~subm} \\
\href{mailto:agshubh191@gmail.com}{agshubh191@gmail.com} 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IIT, Kanpur}
\descript{B.Tech in Computer Science}
\location{Expected Apr 2017 \\ CPI: 8.9}
\sectionsep

\subsection{Pre University}
\location{St. Joseph's School, Kota, Rajasthan}
\descript{Grade $12^{th}$}
Percentage: \textbf{94}

\descript{Grade $10^{th}$}
CGPA: \textbf{10}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github://submagr \href{https://github.com/submagr} \\
LinkedIn://shubham-agrawal \href{https://www.linkedin.com/in/shubham-agrawal-5b002ab2} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Machine Learning Tools \\
Natural Language Processing \\
Recent Advances in Vision \\
Optimizations Techniques \\
Operating Systems | A* \\
Compiler Design \\
Computer Networks \\ 
Computer Security \\

Computer Organization \\
Advanced Algorithms \\
Data Structures and Algorithms \\
Theory of Computation \\

Linear Algebra \\
Discrete Mathematics \\
Abstract Algebra \\
Probability and Statistics \\


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Python \textbullet{} C \textbullet{} C++ \\
\location{Over 1000 lines:}
Go \textbullet{} Javascript \textbullet{} CSS \textbullet{} HTML \textbullet{} PHP \\
MySQL \textbullet{} MongoDB \\
\location{Familiar:}
Matlab \textbullet Material Design 
\sectionsep

\subsection{Libraries}
Keras, Theano, Scikit-Learn, Caffe
\sectionsep

\subsection{Tools}
Vim, Solidworks, Linux, Windows
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 


\section{Awards} 
\begin{tabular}{rll}
	2013 & All India Rank 191 & IIT-JEE ADVANCED among 1,50,000 candidates \\
	2013 & All India Rank 1234 & JEE-MAINS among 14, 00,000 candidates \\ 
	2014 & Academic Excellence Award & DOAA, IIT Kanpur \\
	2015 & BEST ROOKIE TEAM  & BAJA STUDENT INDIA \\ 
\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience and Projects}

\runsubsection{Adobe}
\descript{| Research Intern}
\location{May-July 2016 | Big Data Experience Lab, Bangalore}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item User affinitGeo-fences are created by identifying areas with high values of user interest. To unsheathe interest from sparse location tagged browsing data, algorithm captures intrinsic interest of user, trends at semantically similar locations and similarity between products and users.

\item Achieved precision was 5 times higher than existing geo-fence. Created user-friendly marketer’s dashboard where marketer can manage geo-fence and get useful inferences about product sale. We will soon be submitting paper and filing patent
\end{tightemize}
\sectionsep

\runsubsection{Pariksha.co}
\descript{| Research + Web Developement Intern}
\location{May-July 2015| Pune}
\begin{tightemize}
\item Engineered an algorithm that adaptively recommend questions depending upon student’s performance and question ratings.
\item Modeled and programmed scalable adaptive question recommender system using GO language and MongoDB database as a micro service.
\item Implemented Pariksha Practice Section for adaptive content and a Gamification engine with impact on 20K students
\end{tightemize}

\runsubsection{Multiple Kernel Learning}
\descript{| Undergraduate project }
\location{Jan - Apr 2015 | IIT Kanpur}
\begin{tightemize}
	\item  Explored relative kernel hilbert space, multiple kernel learning algorithm and hierarchical kernel learning. Project was focused around multiple kernel learning to analyze effects of linear combination of different kernels over classifier.
	\item Extracted surf and convolutional deep-net (pre-trained BVLC GoogleNet model) features for Caltech multiclass object classification dataset containing 102 categories. Implemented Simple MKL algorithm and studied effects of linear combination of distinct kernels on svm classifier.
\end{tightemize}
\sectionsep

\runsubsection{Course Projects}
\\
\vspace{\topsep} 
\begin{tabular}{ll}
	Optimization & \\
	Vision & \\
	NLP & \\
	MLT & \\
	Compiler & \\
	OS & \\ 
\end{tabular}
\sectionsep

\section{Miscellaneous} 

\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}